---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- date: "24 de Septiembre de 2020" -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```


# An R package to play with Fortran and OpenMP

I want to learn more R+Fortran so I created this package to play with R+Fortran

**ALWAYS READ THE [R-EXTS](https://cran.r-project.org/doc/manuals/r-release/R-exts.html) MANUAL**

Functions:

**R:**
```{r}
library(rfortran)
get_threads()
```

**Fortran:**
```{fortran, eval = F}
SUBROUTINE checkntf (nt) ! # nocov start
USE OMP_LIB
IMPLICIT NONE


INTEGER nt


nt = OMP_GET_MAX_THREADS()

RETURN
END ! # nocov end

```



**Makevars:**

```{bash,eval = FALSE}
USE_FC_TO_LINK =
PKG_FFLAGS = $(SHLIB_OPENMP_FFLAGS)
PKG_LIBS = $(SHLIB_OPENMP_FFLAGS)


C_OBJS = init.o
FT_OBJS = get_threads.o

all:
	@$(MAKE) $(SHLIB)
	@rm -f  *.o

$(SHLIB): $(FT_OBJS) $(C_OBJS)

init.o:  get_threads.o

```

**C: generated with `tools::package_native_routine_registration_skeleton(".")`**

init.c

```{c,eval = FALSE}
#include <R_ext/RS.h>
#include <stdlib.h> // for NULL
#include <R_ext/Rdynload.h>

/* FIXME: 
   Check these declarations against the C/Fortran source code.
*/

/* .Fortran calls */
extern void F77_NAME(checkntf)(void *);

static const R_FortranMethodDef FortranEntries[] = {
    {"checkntf", (DL_FUNC) &F77_NAME(checkntf), 1},
    {NULL, NULL, 0}
};

void R_init_rfortran(DllInfo *dll)
{
    R_registerRoutines(dll, NULL, NULL, FortranEntries, NULL);
    R_useDynamicSymbols(dll, FALSE);
}

```


## Add plays

If you know any play, fortran subroutine, trick or anything let me know, make a [pull request](https://github.com/ibarraespinosa/rfortran/pulls) or anything
